---
title: "msiCompare--A package for class comparison for mass spectrometry imaging data"
author: "April J Harry"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msiCompare--A package for class comparison for mass spectrometry imaging data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction

*Purpose
*this is a demonstration of functionality
*overview of features and availability

```{r, fig.show='hold',results='hide'}
library(msiCompare)
```

# Integration with *Cardinal*
```{r, fig.show='hold',results='hide'}
library(Cardinal)
```

# Simulating MS images
## Model-based simulation

```{r, fig.show='hold',cache=TRUE}
conditions <- ifelse((expand.grid(x=1:30, y=1:30)$x %in% (1+floor(30/5)):(30-floor(30/5)) & expand.grid(x=1:30, y=1:30)$y %in% (1+floor(30/5)):(30-floor(30/5))), 2, 1)

 s <- simSingle(
      reps = 3,
      diff = log2(1.5),
      tau2 = 0.1,
      sig2 = 0.1,
      seed = 8372,
      size1 = 30,
      center.pattern = T,
      pattern = conditions
      )
```

```{r, fig.show='hold'}
summary(s)
```

```{r, fig.show='hold'}
image(s$simSet, feature = 1)
```

```{r, fig.show='hold',cache=TRUE}
 s_multi <- simMulti(
      sampleVar = 0.1,
      reps = 1,
      diff = log2(1.5),
      tau2 = 0.1,
      sig2 = 0.1,
      seed = 8372,
      size1 = 30,
      size2 = 30^2,
      numHealthy = 3,
      numDisease = 3)

image(s_multi$simSet, feature = 1, layout = c(3,2))
```

# Examples of class comparison
## Hiearchical Bayesian Spatial Model
* show compareMSI
```{r, fig.show='hold',cache=TRUE}
fitHBSM <- compareMSI(msset = s_multi$simSet,
           conditionOfInterest = s_multi$simSet$diagnosis,
           techRep = s_multi$simSet$sample,
           feature = 1,
           nsim = 5000, burnin=2500,
           trace = F, dropZeros = T)

fitHBSM$Feature1$gamma
```
*note hiearchical centering
*bfdr adjustment


## Location-wise ANOVA
```{r, fig.show='hold',cache=TRUE}
summary(lm(c(spectra(s_multi$simSet)[1,]) ~ s_multi$simSet$diagnosis))
```
```{r, fig.show='hold',cache=TRUE}
p_averaging(s_multi$simSet)
```


## Cassese et al
```{r, fig.show='hold',cache=TRUE}
fit_spautolm <- cass(msset = s$simSet, roiFactor = factor(s$simSet$diagnosis),
     logscale = F, thresholds = 1:5)

fit_spautolm$results$CAR_AIC_min_pvalues
```
*cite
*show their model


